Local PCA Shows How the Effect of Population Structure Differs Along the Genome

### 2018-08-08 writeup/local_pca_paper.tex
latex wrangling
add sup figures

\newif\ifsubmission
% \submissiontrue
\submissionfalse
\ifsubmission
    % % stuff for submission
    \usepackage[nofiglist,nomarkers,figuresonly]{endfloat}
    \usepackage{setspace}
    \doublespacing
    \usepackage{lineno}
    \linenumbers
    \bibliographystyle{plos2015}
    \newcommand\citet{\cite}
    \newcommand\citep{\cite}
    \renewcommand\includegraphics{\relax}
    \renewcommand{\includegraphics}[2][]{\relax}
    \renewcommand{\figurename}{Fig.}
    \newcommand{\Figure}{Fig }
    \newcommand{\Figures}{Fig }
\else
    % for the nice version
    \usepackage[square,sort,comma,numbers]{natbib} \bibpunct{(}{)}{;}{author-year}{}{,} 
    \bibliographystyle{plainnat}
    \newcommand{\Figure}{{Figure }}
    \newcommand{\Figures}{{Figures }}
\fi
% grrr
\newcommand{\citetx}[2][]{\ifsubmission#1 \cite{#2}\else\citet{#2}\fi}

@@

@@

\begin{table}[ht]
\centering
    \begin{tabular}{p{0.8in}rrrr}
  \hline
    species 
    & \parbox[t]{.8in}{\# SNPs per \\ window} 
    & \parbox[t]{1in}{mean window\\ length (bp)}
    & \parbox[t]{1.2in}{mean \# windows \\ per chromosome} 
    & \parbox[t]{1.4in}{mean \% variance ex-\\plained by top 2 PCs} \\ 
  \hline
  \textit{Drosophila melanogaster} & 1,000 & 9,019 & 2,674 & 0.53 \\ 
  Human & 100 & 636,494 & 203 & 0.55 \\ 
  \textit{Medicago truncatula} & 10,000 & 102,580 & 467 & 0.50 \\ 
   \hline
\end{tabular}
\caption{
    Descriptive statistics for each dataset used.
    \revpoint{2}{18}
    % % with the chosen window sizes.
    % % See text for how window sizes were chosen;
    % Columns 2--4 give statistics describing the window sizes used for most analyses for each dataset
    % (windows had a fixed number of SNPs).
    % The final column gives the percent variance explained by the top two principal components,
    % averaged across independent PCA of each window.
    \label{tab:data_stats}
}
\end{table}

@@

>>>>

\newif\ifsubmission
\submissiontrue
% \submissionfalse
\ifsubmission
    % % stuff for submission
    \usepackage[nofiglist,nomarkers,figuresonly]{endfloat}
    \usepackage{setspace}
    % \doublespacing
    \bibliographystyle{plos2015}
    \newcommand\citet{\cite}
    \newcommand\citep{\cite}
    \renewcommand\includegraphics{\relax}
    \renewcommand{\includegraphics}[2][]{\relax}
    \renewcommand{\figurename}{Fig.}
    \newcommand{\Figure}{Fig }
    \newcommand{\Figures}{Fig }
\else
    % for the nice version
    \usepackage[square,sort,comma,numbers]{natbib} \bibpunct{(}{)}{;}{author-year}{}{,} 
    \bibliographystyle{plainnat}
    \newcommand{\Figure}{{Figure }}
    \newcommand{\Figures}{{Figures }}
    \renewcommand{\linelabel}[1]{}
\fi
% grrr
\newcommand{\citetx}[2][]{\ifsubmission#1 \cite{#2}\else\citet{#2}\fi}

@@

\ifsubmission\linenumbers\fi

@@

\begin{table}[ht]
\centering
    \begin{tabular}{p{0.8in}rrrr}
  \hline
    species 
    & \parbox[t]{.8in}{\# SNPs per \\ window} 
    & \parbox[t]{1in}{mean window\\ length (bp)}
    & \parbox[t]{1.2in}{mean \# windows \\ per chromosome} 
    & \parbox[t]{1.4in}{mean \% variance ex-\\plained by top 2 PCs} \\ 
  \hline
  \textit{Drosophila melanogaster} & 1,000 & 9,019 & 2,674 & 0.53 \\ 
  Human & 100 & 636,494 & 203 & 0.55 \\ 
  \textit{Medicago truncatula} & 10,000 & 102,580 & 467 & 0.50 \\ 
   \hline
\end{tabular}
\caption{
    Descriptive statistics for each dataset used.
    % \revpoint{2}{18}  %% no line numbers here; won't work
    % % with the chosen window sizes.
    % % See text for how window sizes were chosen;
    % Columns 2--4 give statistics describing the window sizes used for most analyses for each dataset
    % (windows had a fixed number of SNPs).
    % The final column gives the percent variance explained by the top two principal components,
    % averaged across independent PCA of each window.
    \label{tab:data_stats}
}
\end{table}

@@

%%%%%%%%%%simulations

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_012720}
    \end{center}
    \caption{
        MDS visualizations of simulation run_012720 (RECOMBTYPE, ``step"; SELTYPE, ``neutral")
        \label{sfig:mds_run_012720}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_027034}
    \end{center}
    \caption{
        MDS visualizations of simulation run_027034 (RECOMBTYPE, ``base"; SELTYPE, ``neutral")
        \label{sfig:mds_run_027034}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_015598}
    \end{center}
    \caption{
        MDS visualizations of simulation run_015598 (RECOMBTYPE, ``hotspot"; SELTYPE, ``neutral")
        \label{sfig:mds_run_015598}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corner_pca-1_run_015598}
    \end{center}
    \caption{
        PCA plots for regions colored in \Figure \ref{sfig:mds_run_015598}
        \label{sfig:pca_corner_run_015598}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_005464}
    \end{center}
    \caption{
        MDS visualizations of simulation run_005464 (RECOMBTYPE, ``base"; SELTYPE, ``selected")
        \label{sfig:mds_run_005464}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_031486}
    \end{center}
    \caption{
        MDS visualizations of simulation run_031486 (RECOMBTYPE, ``base"; SELTYPE, ``selected")
        \label{sfig:mds_run_031486}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_009673}
    \end{center}
    \caption{
        MDS visualizations of simulation run_009673 (RECOMBTYPE, ``step"; SELTYPE, ``selected")
        \label{sfig:mds_run_009673}
    }
\end{figure}
